Online Verification of Commutativity

### 2020-08-10 acmPaper/paper.tex
idk
Added space complexity

The notation $\partial(p)$ maps to the tuple (start node of $p$, end node of $p$).
$\partial(p)^{+}$ is the start node, and $\partial(p)^{-}$ is end node).

@@

An efficient implementation of the algorithm can run in $O(|V|^2(|V|+|E|))$ time at a $O(|V|^3)$ space cost. In such an implementation, path finding from a given source node to all potential sink nodes could be done in a single $O(|V|+|E|)$ breadth first search and the results memoized in $O(|V|^2)$ space.

@@

The run time of the first step is $O(|V|^4)$, and that of the second step is $O(|V|)$, so that the overall bound is $O(|V|^4)$.

>>>>

The notation $\partial(p)$ maps to the tuple (start node of $p$, end node of $p$).
Additionally, $\partial(p)^{+}$ is the start node, and $\partial(p)^{-}$ is end node of p.

@@

An efficient implementation of the algorithm can run in $O(|V|^2(|V|+|E|))$ time, space complexity not exceeding the asymptotic $O(|V|^2)$ bound on the output.
In such an implementation, path finding from a given source node to all potential sink nodes could be done in a single $O(|V|+|E|)$ breadth first search.

@@

The run time of the first step is $O(|V|^4)$, and that of the second step is $O(|V|)$, so that the overall bound is $O(|V|^4)$.
Space complexity remains $O(|V|^2)$.
